### 2020-07-24 README.Rmd
Get ready for submission

The CRAN task View of [Experimental Design](https://cran.r-project.org/web/views/ExperimentalDesign.html) includes many packages rellevant for designing an experiment before collecting data, but none of them provides how to manage them once the samples are already collected.

>>>>

The CRAN task View of [Experimental Design](https://CRAN.R-project.org/view=ExperimentalDesign) includes many packages rellevant for designing an experiment before collecting data, but none of them provides how to manage them once the samples are already collected.
